---
title: Does Lake and Stream Connectivity
subtitle: Control Phosphorus Retention in Lakes?
author: Joseph Stachelek and Patricia Soranno
institute: Michigan State University
date: "2018\\ June"
bibliography: test.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.path = "figures/", dpi=300, fig.height=3, fig.width=3)
```

```{r read_chunks, echo=FALSE}
knitr::read_chunk("scripts/distribution_cartoons.R")
knitr::read_chunk("scripts/nes_map.R")
```

## P retention is important and well-studied

\vspace{-3em}
\begincols[t]

\hfill\column{0.42\textwidth}

\begin{figure}
\includegraphics[width=4cm]{figures/incrementalcumulative.png}
\end{figure}

\hfill\column{0.54\textwidth}

\vspace{2em}

P retention directly controls downstream transport \cite{alexander_estimating_2002}

\vspace{5em}

P retention indirectly controls sediment P accumulation \cite{SondergaardPersistentinternalphosphorus2013}

\stopcols

## P retention is controlled by water residence time \cite{vollenweiderInputoutputModels1975}

\vspace{-4em}

<!-- P retention is primarily controlled by water residence time \cite{vollenweiderInputoutputModels1975}  -->

\begincols

\hfill\column{0.48\textwidth}

\begin{figure}
\includegraphics[width=7cm]{figures/conceptual_p-cycle_pt1.png}
\end{figure}

\hfill\column{0.52\textwidth}

```{r milstead, echo=FALSE, warning=FALSE, fig.width=3, fig.height=2.5, cache=TRUE}
library(ggplot2)

dt_path <- paste0("~/Documents/Science/Dissertation/Analysis/_episodes_rmd/misc", 
                  "/milstead_x_lagos.rds")

test3 <- readRDS(dt_path)

levels(test3$lakeconnectivity)[1:2] <- c("Secondary", "Primary")
test3 <- test3[test3$hrt > 0,] 
test3 <- test3[test3$AreaSqKm > 0.04,] # rm less than 4 ha
test3 <- test3[!is.na(test3$lakeconnectivity),]

yr_labels <- c("1e-07", "1e-05", 
               as.character(10/365), 
               as.character(2/12),
               "2", "10")

format_labels <- function(x, mult_factor){
  gsub("\\.+$", "\\1", gsub("0+$", "\\1",
    trimws(format(round(as.numeric(x), 6) * 
      mult_factor, scientific = FALSE)), perl = TRUE))
  }

day_labels   <- ceiling(as.numeric(
  format_labels(yr_labels, 365)) / 10) * 10
minute_labels  <- ceiling(as.numeric(
  format_labels(yr_labels, 365 * 24 * 60)) / 10) * 10
month_labels  <- round(as.numeric(
  format_labels(yr_labels, 12)), 0)

mixed_labels <- paste0(
      c(minute_labels[1:2], day_labels[3], month_labels[4], yr_labels[5:6]), 
      c(" min", " min", " days", " months", " years", " years"))

quants <- exp(quantile(log(test3[!is.na(test3$lakeconnectivity), "hrt"])))

ggplot(data = test3, 
    aes(x = hrt, y = Rp)) + geom_point(size = 0.9) +
  scale_x_log10(labels = mixed_labels, 
    breaks = as.numeric(yr_labels), limits = c(1 / 365, 11)) +
  stat_smooth(method = "glm", method.args = list(family = "binomial"), 
              se = TRUE) +
  scale_color_brewer(palette = "Set1") +
  cowplot::theme_cowplot() + 
  theme(legend.position = "none", 
        legend.title = element_blank(), 
        legend.text = element_text(),
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 9), 
        axis.title = element_text(size = 10), 
        panel.background = element_rect(fill = "transparent"), 
        plot.background = element_rect(
          color = "transparent", 
          fill = "transparent"), 
        panel.border = element_blank()) +
  xlab("Residence Time") +
  ylab("P Retention") + 
  annotate("text", label = "Data from Milstead et al. (2013)", x = 1, y = 1, size = 2)
```

\stopcols

## What are some other potential controls on P retention?

\vspace{-1em}

\includegraphics[width=0.9\textwidth]{figures/conceptual_p-cycle_pt2.png}

## Multiple ways to define connectivity

\vspace{-2em}

\includegraphics[width=1\textwidth, left]{figures/conny_metric_key1.png}

\vspace{1em}

\includegraphics[width=1\textwidth]{figures/conny_metric_key2.png}

## What is an appropriate scale for measuring connectivity?

\includegraphics[width=0.6\textwidth]{figures/iws_nws.pdf}

## {.plain}

\plain {Does connectivity of lakes and their watersheds influence lake phosphorus retention?}{What is the relative importance of \alert{different connectivity types} in determining lake P retention and \alert{what spatial extents are most important} for connectivity and P retention?}

## Methods

\vspace{-1em}

\begincols

\hfill\column{0.5\textwidth}

```{r nes_map, echo=FALSE, message=FALSE, warning=FALSE}

```

\hfill\column{0.5\textwidth}

```{r distribution_cartoons, echo=FALSE, message=FALSE, warning=FALSE}

```

\stopcols

## Distributions of P loading model processing coefficients

\vspace{-1em}

\includegraphics[width=0.9\textwidth]{figures/06_k-1.pdf}

## Results table of delta k's

## Connectivity of lakes and their watersheds is related to P retention.

\begincols

\hfill\column{0.5\textwidth}

\includegraphics[width=0.6\textwidth]{figures/conceptual_p-cycle_pt5.png}

\hfill\column{0.5\textwidth}

Connectivity at the network (broader) scale is more important than connectivity at finer scales.

\stopcols

<!-- \setlength{\TPHorizModule}{\paperwidth}\setlength{\TPVertModule}{\paperheight} -->
<!-- \begin{textblock}{0.8}(0.3,0.85) -->
<!-- \end{textblock} -->
 
<!-- \setlength{\TPHorizModule}{\paperwidth}\setlength{\TPVertModule}{\paperheight} -->
<!-- \begin{textblock}{0.8}(0.3,0.85) -->
<!--   Lake-watershed connectivity related to watershed area -->
<!--  \end{textblock} -->

<!-- * Watershed controls on P delivery to lakes -->

<!-- * WS:LA ratio -->
