---
title: Does Lake and Stream Connectivity
subtitle: Control Phosphorus Retention in Lakes?
author: Joseph Stachelek and Patricia Soranno
institute: Michigan State University
date: "Assoc. Limnology and Oceanography, 2018\\ June"
bibliography: test.bib
nocite: | 
  @MilsteadEstimatingSummerNutrient2013
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.path = "figures/", dpi=300, fig.height=3, fig.width=3)
```

```{r read_chunks, echo=FALSE}
knitr::read_chunk("scripts/distribution_cartoons.R")
knitr::read_chunk("scripts/nes_map.R")
```

## Lake phosphorus (P) retention
 <!-- is important and well-studied -->

\vspace{-2em}

\begincols

\hfill\column{0.42\textwidth}

\begin{figure}
\includegraphics[width=4cm]{figures/incrementalcumulative.png}
\end{figure}

\hfill\column{0.54\textwidth}

P retention directly controls downstream transport \cite{alexander_estimating_2002}

\vspace{5em}

P retention indirectly controls sediment P accumulation \cite{SondergaardPersistentinternalphosphorus2013}

\stopcols

## Predicting flux is complex
\vspace{-3em}
\centering
\includegraphics[width=10cm]{figures/pihm.png}\cite{bhatt2014tightly}

<!--  \setlength{\TPHorizModule}{\paperwidth}\setlength{\TPVertModule}{\paperheight} -->
<!-- \begin{textblock}{0.7}(0.5,0.17) -->
<!--   <!-- Only possible for a limited  \\ number of lakes --> -->
<!--  \end{textblock} -->

## P retention conceptual model

\vspace{-4em}

<!-- P retention is primarily controlled by water residence time \cite{vollenweiderInputoutputModels1975}  -->

\begin{figure}
\includegraphics[width=8cm]{figures/conceptual_p-cycle_pt1.png}
\end{figure}

## P retention versus water residence time
\vspace{-2em}

\nocite{MilsteadEstimatingSummerNutrient2013}
\centering
```{r milstead, echo=FALSE, warning=FALSE, fig.width=4, fig.height=3.3, cache=TRUE}
library(ggplot2)

dt_path <- paste0("~/Documents/Science/Dissertation/Analysis/_episodes_rmd/misc", 
                  "/milstead_x_lagos.rds")

test3 <- readRDS(dt_path)

levels(test3$lakeconnectivity)[1:2] <- c("Secondary", "Primary")
test3 <- test3[test3$hrt > 0,] 
test3 <- test3[test3$AreaSqKm > 0.04,] # rm less than 4 ha
test3 <- test3[!is.na(test3$lakeconnectivity),]

yr_labels <- c("1e-07", "1e-05", 
               as.character(10/365), 
               as.character(2/12),
               "2", "10")

format_labels <- function(x, mult_factor){
  gsub("\\.+$", "\\1", gsub("0+$", "\\1",
    trimws(format(round(as.numeric(x), 6) * 
      mult_factor, scientific = FALSE)), perl = TRUE))
  }

day_labels   <- ceiling(as.numeric(
  format_labels(yr_labels, 365)) / 10) * 10
minute_labels  <- ceiling(as.numeric(
  format_labels(yr_labels, 365 * 24 * 60)) / 10) * 10
month_labels  <- round(as.numeric(
  format_labels(yr_labels, 12)), 0)

mixed_labels <- paste0(
      c(minute_labels[1:2], day_labels[3], month_labels[4], yr_labels[5:6]), 
      c(" min", " min", " days", " months", " years", " years"))

quants <- exp(quantile(log(test3[!is.na(test3$lakeconnectivity), "hrt"])))

ggplot(data = test3, 
    aes(x = hrt, y = Rp)) + geom_point(size = 0.9) +
  scale_x_log10(labels = mixed_labels, 
    breaks = as.numeric(yr_labels), limits = c(1 / 365, 11)) +
  stat_smooth(method = "glm", method.args = list(family = "binomial"), 
              se = TRUE) +
  scale_color_brewer(palette = "Set1") +
  cowplot::theme_cowplot() + 
  theme(legend.position = "none", 
        legend.title = element_blank(), 
        legend.text = element_text(),
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 9), 
        axis.title = element_text(size = 10), 
        panel.background = element_rect(fill = "transparent"), 
        plot.background = element_rect(
          color = "transparent", 
          fill = "transparent"), 
        panel.border = element_blank()) +
  xlab("Residence Time") +
  ylab("P Retention") + 
  annotate("text", label = "Data from Milstead et al. (2013)", x = 1, y = 1, size = 2)
```

## Extending P retention models

<!-- What are some other potential controls on P retention? -->

\vspace{-1em}

\includegraphics[width=0.9\textwidth]{figures/conceptual_p-cycle_pt2.png}

## Multiple ways to define connectivity

\vspace{-2em}

\setlength{\TPHorizModule}{\paperwidth}\setlength{\TPVertModule}{\paperheight}
\begin{textblock}{0.7}(0.5,0.17)
  Low Connectivity  \hspace{2em}  High Connectivity
 \end{textblock}

\includegraphics[width=1\textwidth, left]{figures/conny_metric_key1.png}

\vspace{1em}

\includegraphics[width=1\textwidth]{figures/conny_metric_key2.png}

## Watershed connections

<!-- What is an appropriate scale for measuring connectivity? -->

\vspace{-2em}

\begincols

\hfill\column{0.6\textwidth}

\centering
\includegraphics[width=\textwidth]{figures/iws_nws.pdf}

\hfill\column{0.4\textwidth}


\stopcols

## Watershed connections

<!-- What is an appropriate scale for measuring connectivity? -->

\vspace{-2em}

\begincols

\hfill\column{0.6\textwidth}

\centering
\includegraphics[width=\textwidth]{figures/iws_nws.pdf}

\hfill\column{0.4\textwidth}

\includegraphics[width=\textwidth]{figures/iws_vs_nws-gis-1.pdf}

\stopcols

## {.plain}

\plain{1. Does connectivity of lakes and their watersheds influence lake phosphorus retention?}{2. What is the relative importance of \texttt{different connectivity metrics} in determining lake P retention and \alert{what spatial extents are most important} for connectivity and P retention?}

## Methods - Connectivity partitions

\vspace{-2em}

\begincols

\hfill\column{0.5\textwidth}

```{r nes_map, echo=FALSE, message=FALSE, warning=FALSE}

```

\hfill\column{0.5\textwidth}

\centering

<!-- \includegraphics[width=0.5\textwidth]{figures/plot_tree_example-1.pdf} -->

<!-- \vspace{1em} -->

\includegraphics[width=0.8\textwidth]{figures/partition_example_scatter-1.pdf}

\stopcols

## Methods - P retention modelling

\vspace{-1em}

\begincols

\hfill\column{0.55\textwidth}

\includegraphics[width=\textwidth]{figures/best_partition_maps-1.png}

\hfill\column{0.45\textwidth}

```{r distribution_cartoons, echo=FALSE, message=FALSE, warning=FALSE, fig.width=2.5}

```

\stopcols

## P retention (processing) coefficient distributions

\vspace{-1em}
\centering

\includegraphics[width=\textwidth]{figures/06_k-3.pdf}

## Conclusion

\nocite{stacheleksoranno}

\vspace{-2em}

\includegraphics[width=0.9\textwidth]{figures/conceptual_p-cycle_pt2.png}

\setlength{\TPHorizModule}{\paperwidth}\setlength{\TPVertModule}{\paperheight}
\begin{textblock}{0.7}(0.35,0.78)
Connectivity metrics at the network scale \\ have a greater effect on P retention than \\ metrics at finer scales.
 \end{textblock}

## Implications

<!-- * WS:LA ratio -->
\centering
\includegraphics[width=0.4\textwidth]{figures/iws_vs_nws-gis-1.pdf}

<!-- \setlength{\TPHorizModule}{\paperwidth}\setlength{\TPVertModule}{\paperheight} -->
<!-- \begin{textblock}{0.8}(0.3,0.85) -->
<!--   Lake-watershed connectivity related to watershed area -->
<!--  \end{textblock} -->

<!-- * Watershed controls on P delivery to lakes -->
